---
title: "Classification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Classification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation

```{r}
# devtools::install_github("https://github.com/MatthiasUckert/RsClassification")
```

# Library

```{r setup}
library(RsClassification); library(fs); library(openxlsx); library(kableExtra)
```

# Overview

Really short description on how to use the ***RsClassification*** library

## Example Project  

The library includes a test project as reference. The project can be downloaded with the ***download_example_project()*** function (see below).

```{r}
RsClassification::download_example_project(
  .dir = "FULL_PATH_TO_LOCAL_FOLDER",
  .name = "TEST PROJECT"
)
```

A project must always contain one excel workbook (Excel Name: input.xlsx) and a folder with documents (Folder Name: docs). The name of the parent folder is used as the general project name.

The test project underlying data can also be accessed:

```{r}
.dir <- system.file("extdata/test_project", package = "RsClassification")
fs::dir_tree(.dir)

```

The input xlsx must contain two sheets:

-   Sheet 1: IDs

    -   The ***IDs***sheet contains a table that lists all entries to classify (id 1:n) and the attributes you want to assign to each entry (column names).

    -   Additionally in row (id = 0) you can specify the column types (numeric, date, checkbox, select, dropdown, autocomplete, password, and handsontable (not implemented yet), see rhandsontable::hot_col(type).

    -   IDs must be unique

-   Sheet 2: Documents

    -   In the ***Documents*** sheet to you can map any document in the docs folder to an IDs in the ***IDs***sheet

The example file looks like this

```{r}
.path <- file.path(.dir, "input.xlsx")
tab_ids  <- read.xlsx(.path, "IDs")
tab_docs <- read.xlsx(.path, "Documents")

```

IDs Sheet

```{r}
tab_ids %>% kbl() %>% kable_paper(full_width = FALSE)
```

Documents Sheet

```{r}
tab_docs %>% kbl() %>% kable_paper(full_width = FALSE)
```

You can start classifying by using the ***run_app()*** function

```{r message=FALSE, warning=FALSE}
# RsClassification::run_app()
```

The rest is hopefully self explanatory :-D

Library will be heavily updated over the next weeks/months. Hopefully not so many breaking changes
